TacticToe: Learning to Prove with Tactics

### 2018-08-20 tactictoe_jv.tex
Proof plan draft

\textsf{ML4PG}~\cite{DBLP:journals/corr/abs-1212-3618,DBLP:journals/mics/HerasK14}
groups related proofs using clustering
algorithms. It allows \coq users to inspire themselves from similar proofs and
notice duplicated proofs. Comparatively, our predictions come from a much more
detailed description of the target goal. \tactictoe can also organize the
predictions to produce verifiable proofs and is not restricted to user
advice.
%However, we simply create a single label for each tactic call whereas each of
%its
%arguments is treated independently in \textsf{ML4PG}.
%Our choice is motivated by the k-NN algorithm already used in
%\holyhammer for the a of theorems.
%, which can be easly adapted to the selection of tactics but would be improved
%by a
%version that can learn to predict tactics and their arguments independently.

@@

It is important to consider the strength of the language used for building 
proofs and proof procedures when designing a system such as \tactictoe. Indeed, 
such system will be re-using those procedures.
In \isabelle, the language {\textsf{Eisbach}\xspace}~\cite{eisbach} was created 
on top of the standard tactic language by giving access to constructors of the 
tactic language to the end-user. The language 
{\textsf{PSL}\xspace}~\cite{NagashimaK17psl} was also developed. It can combine 
regular tactics and tools such as \sledgehammer.
In \coq, the \ltac~\cite{ltac} meta language was designed to enrich the 
tactic combinators of the \coq language. It adds functionalities such as 
recursors and matching operators for terms and proof contexts.
In \holfour, the strength of \sml as a proof strategy 
language has been demonstrated by the implementation of complex proof 
procedures such as \metis. 
% TODO: Add a sentence about try-hard

%Comparatively, in \holfour, new tactics can be written by end-users in the 
%implementation 
%language \sml. Therefore, the design of a meta language was 
%not necessary as every proof method is a \sml function. 
%Using this language, the authors 
%created a default search strategy ``try-hard'' that includes calls to 
%\sledgehammer, and that outperforms \sledgehammer.

>>>>

\textsf{ML4PG}~\cite{DBLP:journals/corr/abs-1212-3618,DBLP:journals/mics/HerasK14}
groups related proofs using clustering
algorithms. It allows \coq users to inspire themselves from similar proofs and
notice duplicated proofs. Comparatively, our predictions come from a much more
detailed description of the target goal. \tactictoe can also organize the
predictions to produce verifiable proofs and is not restricted to user
advice.

A closely related approach is proof planning that was firstly describe in 
~\cite{}. Proof planning is a meta approach to tactics constructing more and 
more general tactics by sharing common proof patterns between different tactics.
Comparatively, our approach tries to automate the construction of proof plans 
by letting MCTS policy decide which tactics is the best in each situation. Our 
approach can be thought as one general proof plan only guided by previous human 
proofs. 
From another angle, if we think of proof plans as ``domain'' specific tactics 
our approach does not try to synthetize proof plan automatically but just 
re-use them if they already exists.

%However, we simply create a single label for each tactic call whereas each of
%its
%arguments is treated independently in \textsf{ML4PG}.
%Our choice is motivated by the k-NN algorithm already used in
%\holyhammer for the a of theorems.
%, which can be easly adapted to the selection of tactics but would be improved
%by a
%version that can learn to predict tactics and their arguments independently.

@@

It is important to consider the strength of the language used for building 
proofs and proof procedures when designing a system such as \tactictoe. Indeed, 
such system will be re-using those procedures.
In \isabelle, the language {\textsf{Eisbach}\xspace}~\cite{eisbach} was created 
on top of the standard tactic language by giving access to constructors of the 
tactic language to the end-user. The language 
{\textsf{PSL}\xspace}~\cite{NagashimaK17psl} was also developed. It can combine 
regular tactics and tools such as \sledgehammer.
In \coq, the \ltac~\cite{ltac} meta language was designed to enrich the 
tactic combinators of the \coq language. It adds functionalities such as 
recursors and matching operators for terms and proof contexts.
In \holfour, the strength of \sml as a proof strategy 
language has been demonstrated by the implementation of complex proof 
procedures such as \metis.
